%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	10pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font
\usepackage[hidelinks]{hyperref} % For hyperlinks
\usepackage{fontawesome} % For icons
\let\orighref\href
\renewcommand{\href}[2]{\orighref{#1}{#2\,\faExternalLink}}

%------------------------------------------------

\name{Sean Murphy} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

% \address{smurphnerd.com} % Main address

% \address{123 Pleasant Lane \\ City, State 12345} % A secondary address (optional)

\address{0468~$\cdot$~340~$\cdot$~941 \\ smur0055@student.monash.edu} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

	\textbf{Monash University} \hfill \textit{Graduating December 2025} \\
	Master of Artificial Intelligence \\
	Current WAM: 93 \\
	FIT5215 Deep Learning Kaggle Competition Winner

	\textbf{Swinburne University of Technology} \hfill \textit{December 2023} \\
	B.S. in Accounting and Business IT \\
	Vice Chancellor's Scholarship Recipient
	% Overall GPA: 3.107 \\

	% \textbf{Melbourne High School} \hfill \textit{December 2020} \\
	% Atar: 97.35

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{AiLECS Researcher}{February 2025 - Present}{Monash University}{Melbourne, VIC}
		\item Conducting research in AI interpretability methods, focusing on making deep learning models more transparent and understandable
		\item Performing comprehensive literature reviews and prototyping potential solutions for neural network analysis
		\item Contributing to research planning and methodology development for upcoming implementations in model interpretability
	\end{rSubsection}

	%-------------------------------------------------

	\begin{rSubsection}{Lead Developer}{November 2022 - Present}{iLearn Education}{Melbourne, VIC}
		\item Leading a team of 3 developers in designing, building, and deploying full-stack solutions for an educational platform.
		\item Collaborating closely with clients to gather and refine business requirements, translating them into detailed technical specifications for development.
		\item Researching and implemented emerging technologies, tools and frameworks for use in the platform.
		\item Maintaining documentation to keep development aligned with project goals, ensuring seamless onboarding and knowledge transfer.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{Software Developer}{January 2023 - December 2023}{SeventhBeam}{Fitzroy, VIC}
		\item Developed dynamic mobile and web applications with Flutter, Firebase, and React, enhancing user interactivity and platform performance.
		\item Engineered robust backend services using Golang and PostgreSQL, ensuring scalability and efficient data management for mobile and web applications.
		\item Set up automated CI/CD pipelines to streamline the development process, integrating tools for testing, building, and deployment.
		\item Collaborated in an agile development team, participating in sprints and cross-functional collaboration to deliver high-quality software solutions.	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

	% \begin{rSubsection}{Multiagent Reinforcement Learning Pathfinding}{October 2024}{FIT5226}{}
	% 	\item Wrote a Python implementation of a multiagent reinforcement learning algorithm for pathfinding using a Deep Q-Network (DQN).
	% 	\item Developed visualizations to demonstrate the algorithm's performance in a gridworld environment, showcasing the agents' ability to learn optimal paths.
	% 	\item Achieved 100\% on all evaluation metrics given by the task description.
	% \end{rSubsection}

	%------------------------------------------------

	% \begin{rSubsection}{Image Classification Kaggle Competition}{August - September 2024}{FIT5215}{}
	% 	\item Used PyTorch and Transformers to develop various deep learning models for image classification, achieving 100\% accuracy on the test set.
	% 	\item Researched and implemented state-of-the-art techniques in image classification, including transfer learning, data augmentation, and ensemble modeling.
	% \end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{\href{https://ilearneducation.com.au/}{iLearn Education Platform}}{February 2023 - Present}{iLearn Education}{}
		\item Designed and implemented the backend architecture for an online learning platform using Golang and PostgreSQL.
		% \item Developed an admin dashboard using NextJS, enabling teachers to manage courses and students.
		\item Developed an admin dashboard using NextJS, equipping teachers with tools to manage courses, track student progress, and administrative tasks.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{\href{https://www.smurphnerd.com/projects/why-leave-town}{Why Leave Town Admin Console}}{October - December 2023}{Why Leave Town}{}
		\item Built a user-friendly platform for businesses to manage and administer gift card programs, simplifying operations and enhancing customer engagement.
		\item Implemented a RESTful API and integrated it with a responsive frontend to ensure efficient data handling and user experience.
		\item Created design patterns in a new codebase to ensure maintainability and scalability.
	\end{rSubsection}

	%------------------------------------------------

	\begin{rSubsection}{\href{https://www.smurphnerd.com/projects/vodalogic}{Vodalogic}}{June - October 2023}{Vodalogic}{}
		\item Led the frontend development of an application for managing IoT devices, ensuring a responsive and intuitive user interface.
		\item Collaborated on the implementation of a hybrid REST and GraphQL API to optimize data retrieval for the frontend.
		\item Managed the deployment of the app to the Google Play Store and Apple App Store.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS AND INTERESTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills \& Interests}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Computer Languages & Python, Golang, SQL, LaTeX, Shell, Typescript \\ % AI
		% Computer Languages & JavaScript, Typescript, Golang, Python, SQL              \\ % SD
		% Software           & PyTorch, Scikit-learn, Transformers, Docker               \\ % AI
		Software           & Docker, React, NextJS, Tailwind               \\ % SD
		% Tools              & Neovim, Jupyter Lab, Git, GitHub                          \\ % AI
		Tools              & Neovim, Git, GitHub                           \\ % SD
		Interests          & Tetris, Rubik's Cube, Swimming, Calisthenics  \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
